Supplementary Information

### 2020-09-25 writing/transect_supplement.Rmd
add quality profile supplementary figure

>>>>

(ref:qual-check-s) Read quality profiles for different sequencing strategies

(ref:qual-check) **(a)** per-base error rate; **(b)** expected number of errors per read. Statistics are based on quality scores assigned by technology-specific basecallers. **THIS NEEDS TO BE MENTIONED IN THE TEXT (addresses reviewer comment)**

```{r qual-check, fig.cap = "(ref:qual-check-s). (ref:qual-check)", fig.scap = "(ref:qual-check-s)"}
ggpubr::ggarrange(
  readd(erate_plot),
  readd(eexp_plot),
  ncol = 1,
  common.legend = TRUE,
  legend = "bottom",
  labels = "auto"
)
```
